The Local Group in the Cosmic Web

### 2014-10-27 paper/main.tex
version para enviar
fixed minor typo in main

\begin{abstract}
We explore the characteristics of the
cosmic web around Local Group(LG) like pairs  using a cosmological simulation in the
$\Lambda$CDM cosmology.  
We use the Hessian of the gravitational potential to classify regions
on scales of $\sim 2$ Mpc as a peak, sheet, filament or void.  
The sample of LG counterparts is represented by two samples of halo
pairs. 
The first is a general sample composed by pairs with
similar masses and isolation criteria as observed for the LG.  
The second is a subset with additional observed kinematic constraints 
such as relative pair velocity and separation. 
We find that the pairs in the LG sample with all constraints are: (i)
Preferentially   located in filaments and sheets, (ii) Located in in a
narrow range of local overdensity $0<\delta<2$, web ellipticity $0.1<e<1.0$ and
prolateness $-0.4<p<0.4$.  (iii) Strongly aligned with the cosmic web.
The alignments are such that he pair orbital angular momentum tends to
be perpendicular to the smallest tidal eigenvector, $\hat{e}_3$, which
lies along the filament direction or the sheet plane.
A stronger alignment is present for the vector linking the two halos with the vector $\hat{e}_3$. Additionally, we fail to find a strong correlation of the spin of each halo in the pair with the cosmic web.
All these trends are expected to a great extent from the selection on
the LG total mass on the general sample. 
Applied to the observed LG, there is a potential conflict between
the alignments of the different planes of satellites and the numerical
evidence for satellite accretion along filaments; the direction
defined by $\hat{e}_3$. This highlights the relevance of achieving a
precise characterization of the place of the LG in the cosmic web in
the cosmological context provided by $\Lambda$CDM.

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.45\textwidth]{fig5a.pdf}
  \includegraphics[width=0.45\textwidth]{fig5b.pdf}
\caption{Mass dependency of the median value for the dot product
  between the normal/radial vector $\hat{n}$/$\hat{r}$ (left/right)
  and each one of the  eigenvectors.  The lines show the trends for
  the general sample. The error bars in the 2$\sigma$ and 3$\sigma$ points
  correspond to jackknife estimates. 
  The shaded region shows the expectation for a random distribution
 without any preferential alignment, it encloses the $5\%$ and $95\%$
 percentiles of 10000  flat distributions for $\mu$ generated with the
 same number of points as the $2\sigma$ sample.   
\label{fig:median_alignment_n}}
\end{center}
\end{figure*}

>>>>

\begin{abstract}
We explore the characteristics of the
cosmic web around Local Group(LG) like pairs  using a cosmological simulation in the
$\Lambda$CDM cosmology.  
We use the Hessian of the gravitational potential to classify regions
on scales of $\sim 2$ Mpc as a peak, sheet, filament or void.  
The sample of LG counterparts is represented by two samples of halo
pairs. 
The first is a general sample composed by pairs with
similar masses and isolation criteria as observed for the LG.  
The second is a subset with additional observed kinematic constraints 
such as relative pair velocity and separation. 
We find that the pairs in the LG sample with all constraints are: (i)
Preferentially   located in filaments and sheets, (ii) Located in in a
narrow range of local overdensity $0<\delta<2$, web ellipticity $0.1<e<1.0$ and
prolateness $-0.4<p<0.4$.  (iii) Strongly aligned with the cosmic web.
The alignments are such that the pair orbital angular momentum tends to
be perpendicular to the smallest tidal eigenvector, $\hat{e}_3$, which
lies along the filament direction or the sheet plane.
A stronger alignment is present for the vector linking the two halos with the vector $\hat{e}_3$. Additionally, we fail to find a strong correlation of the spin of each halo in the pair with the cosmic web.
All these trends are expected to a great extent from the selection on
the LG total mass on the general sample. 
Applied to the observed LG, there is a potential conflict between
the alignments of the different planes of satellites and the numerical
evidence for satellite accretion along filaments; the direction
defined by $\hat{e}_3$. This highlights the relevance of achieving a
precise characterization of the place of the LG in the cosmic web in
the cosmological context provided by $\Lambda$CDM.

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.45\textwidth]{fig5.pdf}
  \includegraphics[width=0.45\textwidth]{fig5b.pdf}
\caption{Mass dependency of the median value for the dot product
  between the normal/radial vector $\hat{n}$/$\hat{r}$ (left/right)
  and each one of the  eigenvectors.  The lines show the trends for
  the general sample. The error bars in the 2$\sigma$ and 3$\sigma$ points
  correspond to jackknife estimates. 
  The shaded region shows the expectation for a random distribution
 without any preferential alignment, it encloses the $5\%$ and $95\%$
 percentiles of 10000  flat distributions for $\mu$ generated with the
 same number of points as the $2\sigma$ sample.   
\label{fig:median_alignment_n}}
\end{center}
\end{figure*}
